Push-Pull Signal-Function Functional Reactive Programming

### 2012-11-29 Docs/IFL2012/design.tex
more on 2.4

@@

\todo{What's novel here?  After this section is de-listified need to emphasize that.}

@@

@@

Sets which correspond to signal vectors are built with ``smart'' constructors.
For instance, to construct a set of handlers, individual handling functions are
lifted to handler sets with the {\tt signalHandler} and {\tt eventHandler}
functions, and then combined with each other and {\tt emptyHandler} leaves
using the {\tt combineHandlers} function.

@@

{\tt SFEvalT} actions are constructed using combinators to push events,
update inputs, and step time, as well as actions lifted from the underlying
monad (used to obtain these inputs). An action in the underlying monad
which produces the result and a new state is obtained with the {\tt runSFEvalT}
function.

>>>>

\rn{Evaluation interface: Very cool.  It sounds a bit your FRP implementation itself is kind of
  ``scriptable'' rather than black box...}

@@

\todo{What's novel here?  After this section is de-listified, need to emphasize that.}

@@

\rn{Is the thing that really sets TimeFlies apart?  (Apart from being the first push/pull for SFFRP.)}

@@

Sets which correspond to signal vectors are built with ``smart'' constructors.
For instance, to construct a set of handlers, 
\rn{is this ``set'' the same as the earlier ``vector of actuation functions''?}
individual handling functions are
lifted to handler sets with the {\tt signalHandler} and {\tt eventHandler}
functions, and then combined with each other and {\tt emptyHandler} leaves
using the {\tt combineHandlers} function.
%
\rn{Examples, examples, examples.  There's a lot of prose here that gives the reader some idea, but doesn't
  show them exactly what it would look like.  Too much guesswork required to fill in the gaps.}

@@

{\tt SFEvalT} actions are constructed using combinators to push events,
update inputs, and step time, as well as actions lifted from the underlying
monad (used to obtain these inputs). 
\rn{That sounds introductory... I thought that was supposed to be what we were learning about throughout
  this subsection?}
An action in the underlying monad
which produces the result and a new state is obtained with the {\tt runSFEvalT}
function.
